%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Master's Research Internship} % Job title
    {IRIF, CNRS and  Université Paris Cité} % Organization
    {Paris, France} % Location
    {April, 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Research Internship for M2 of the Masters (MPRI).}
        \item {Guided and supervised by Prof. Iordanis Kerenidis.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {QC Ware Corp.} % Organization
    {Paris, France} % Location
    {August, 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Research Assistant under the guidance of Prof. Iordanis Kerenidis.}
        \item {Provided QML research consultancy and services to various client firms.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Mentor} % Job title
    {Quantum Open Source Foundation} % Organisation
    {Online} % Location
    {September, 2021 - January, 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Mentored a candidate to contribute to the Quantum Protocol Zoo.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Internship} % Job title
    {IRIF, CNRS and  Université Paris Cité} % Organization
    {Paris, France (Remote)} % Location
    {August, 2020 - December, 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Research Internship for completion of Bachelor's Thesis Project.}
        \item {Guided and supervised by Prof. Iordanis Kerenidis.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Undergraduate Research Assistant} % Job title
    {Institute for Quantum Computing, University of Waterloo} % Organization
    {Waterloo, Canada (Remote)} % Location
    {April, 2020 - July, 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Research Assistant under the guidance of Prof. Norbert Lütkenhaus.}
        \item {Associated with Optical Quantum Communication Theory Group.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Internship} % Job title
    {LIP6, CNRS and Sorbonne Université} % Organization
    {Paris, France} % Location
    {May, 2019 - July, 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Summer Research Internship under the guidance of Prof. Elham Kashefi.}
        \item {Part of the Quantum Internet Alliance team at CNRS.}
        \item {Associated with Paris Centre for Quantum Computing.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Chief of Research and Development} % Job title
    {Information Management Group, IIT Roorkee} % Organisation
    {Roorkee, India} % Location
    {January, 2018 - June, 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working with a team of around 50 tech enthusiasts to develop software solutions for the college campus community.}
        \item {Maintain the IIT Roorkee official website with up-to-date technology stack.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}