%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Founder, Core Member, Secretary for the term 2020-21} % Affiliation/role
    {Quantum Computing Group, IIT Roorkee} % Organisation/group
    {Roorkee, India} % Location
    {2020 - 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Established the Quantum Computing reading group under ACM Student Chapter, IIT Roorkee.}
        \item {Conducted QC discussions on various topics from the basics to the advanced.}
        \item {Mentored beginners in the field to explore the various topics systematically.}
    \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Editor and President for the term 2019-20} % Affiliation/role
    {Geek Gazette} % Organisation/group
    {Roorkee, India} % Location
    {2017 - 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Official Tech Magazine based in IIT Roorkee.}
        \item {Managed a group of 80 students divided into four diversely functional cells - Editorial, Design, Finance and Web.}
        \item {Written and edited articles and interviews for 6 issues of the magazine and the \emph{\href{https://geekgazette.iitr.ac.in}{website}}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Mentor} % Affiliation/role
    {Student Mentorship Programme} % Organisation/group
    {Roorkee, India} % Location
    {2019 - 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Personally mentored five freshmen from the CS Department.}
        \item {Individually guided them through personal and academic problems for the entire year.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Dramatist} % Affiliation/role
    {Dramatics Section, IIT Roorkee} % Organisation/group
    {Roorkee, India} % Location
    {2017 - 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Performed one Stage Play and acted as non cast member for three stage and street plays.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Programmer} % Affiliation/role
    {Programming and Algorithms Group} % Organisation/group
    {Roorkee, India} % Location
    {2017 - 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Member of the Competitive Coding club based in IIT Roorkee.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
