%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Bachelor's Thesis; Part of Research at IRIF and QC Ware Corp} % Job title
    {Orthogonal Neural Networks} % Organisation
    {Paris, France (Remote)} % Location
    {August, 2020 - June, 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed an orthogonal neural network architecture inspired by quantum gates.}
        \item {Developed strategies to train the perfectly orthogonal neural networks.}
        \item {Extended it further to actual quantum architecture and bench-mark its performance.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Part of Research Assistantship at IQC, UWaterloo} % Job title
    {Numerical key rate calculator for QKD Protocols} % Organisation
    {Waterloo, Canada (Remote)} % Location
    {April, 2020 - July, 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contributed to the development of the software architecture and wrote protocols fitting into it.}
        \item {Wrote unified algorithms to perform parameter optimisation for various QKD Protocols using numerical methods and optimisation techniques.}
        \item {Used High Performance super-computing clusters of ComputeCanada to evaluate various QKD protocols' key rates for different parameters.}
        \item {Software available in the public domain at \emph{\href{https://openqkdsecurity.wordpress.com/}{https://openqkdsecurity.wordpress.com/}}}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Part of Research Internship at LIP6, Paris} % Job title
    {Quantum Protocol Zoo} % Organisation
    {Paris, France} % Location
    {December, 2018 - July, 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Added various protocols to the online encyclopedia of Quantum Internet Protocols and reviewed many others.}
        \item {Analysed and identified the resource requirements for performing each of the protocols.}
        \item {Developed the 'Knowledge Graphs' - a unified, interactive and user-friendly tool for resource visualisation.}
        \item {Available online at  \emph{\href{https://wiki.veriqloud.fr}{wiki.veriqloud.fr}}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Summer Project} % Job title
    {Linear Cryptanalysis of Substitution-Permutation Network} % Organisation
    {Roorkee, India} % Location
    {May, 2018 - June, 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Learning project under Prof. Sugata Gangopadhyay, Dept. of CSE, IIT Roorkee.}
        \item {Implemented a Substitution-Permutation Network based Block Cipher model.}
        \item {Implemented a linear cryptanalytic attack on the developed cryptosystem for retrieval of certain key bits.}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
